\documentclass[11pt]{article}
\usepackage[letterpaper]{geometry}
\usepackage{calligra}

%\pdfgentounicode=1
\pagenumbering{gobble}

\begin{document}

\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r}
kevinlei@tamu.edu & \textbf{\Large Kevin Lei} & (908) 200-8063 \\
\end{tabular*}
\noindent\rule{\textwidth}{0.4pt}
\vspace{0.5em}
\newline
\noindent Mr. Kai Shen,
\vspace{2em}
\newline
\noindent
I am writing to express my strong interest in the Software Engineering Internship at Google for Summer 2025. 
As a rising junior pursuing a Bachelor of Science in Computer Science at Texas A\&M University, I am excited by the opportunity to contribute to Google's mission of organizing the world's information and making it universally accessible and useful.

\vspace{1em}
\noindent
My academic performance, evidenced by a 4.0 GPA in rigorous courses such as data structures, analysis of algorithms, computer organization, and machine learning, has provided me with a solid theoretical foundation. 
However, it is my passion for self-directed learning and innovation that I believe aligns particularly well with Google's culture of continuous improvement and thinking big.
For instance, to enhance my productivity as a developer, I took the initiative to learn Linux and Vim. This self-directed learning not only improved my efficiency but also deepened my understanding of computer systems, which I believe is crucial for developing scalable and efficient software solutions at Google.

\vspace{1em}
\noindent
My drive to exceed expectations is further exemplified by my work with an astronomy research group at Texas A\&M. 
When tasked with creating a basic matplotlib interface for plotting supernova light curves, I saw an opportunity to deliver greater value. 
I developed a full-fledged Next.js web application with an intuitive user interface, which I then deployed on Vercel to make it accessible to the entire research community. 
Additionally, I organized all the data in a PostgreSQL database, significantly enhancing data management and accessibility for the team. 
This project not only showcases my technical skills but also my ability to understand user needs and deliver comprehensive solutions, qualities that I believe are valued at Google.

\vspace{1em}
\noindent
Thank you for your time and consideration. 
I am enthusiastic about the possibility of bringing my passion for technology, dedication to learning, and drive for innovation to Google. 
I look forward to the opportunity to discuss further, and I am available at your convenience.

\vspace{2em}
\noindent Sincerely,
\vspace{1em}
\newline
\noindent\Large\calligra Kevin Lei


\end{document}